Title here

### 2020-06-23 paper/paper.Rmd
update patricia's notes with [... ppp]

@@

@@

>>>>

[Are we using  projection pursuit/guided tour to better understand the convergency of optimization algorithms visually in combination with the algorithms discussed below? Or we are focusing on the optimisation problem only within the project pursuit context? Some of the problems listed below are also applicable to optimization problem in general too. ppp]

@@

[I would expland this section more as the core contribution. ppp]

@@

[I would add the maths here to describe the simulations. ppp]
